### 2023-12-22 docs/projects/visual-tools/clay-calva-demo-20231216/index.qmd
added clay configurations, rerendered

<div><pre><small><small>source: projects/visual-tools/clay-calva-demo-20231216/notebooks/index.clj</small></small></pre></div>

>>>>

<div><pre><small><small>source: <a href="https://github.com/scicloj/clojure-data-scrapbook/blob/main/projects/visual-tools/clay-calva-demo-20231216/notebooks/index.clj">projects/visual-tools/clay-calva-demo-20231216/notebooks/index.clj</a></small></small></pre></div>

### 2023-12-22 docs/projects/visual-tools/clay-cider-demo-20231217/index.qmd
added clay configurations, rerendered

<div><pre><small><small>source: projects/visual-tools/clay-cider-demo-20231217/notebooks/index.clj</small></small></pre></div>

>>>>

<div><pre><small><small>source: <a href="https://github.com/scicloj/clojure-data-scrapbook/blob/main/projects/visual-tools/clay-cider-demo-20231217/notebooks/index.clj">projects/visual-tools/clay-cider-demo-20231217/notebooks/index.clj</a></small></small></pre></div>
